Paper 1 Analysis

### 2016-02-10 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Including one more decimal place.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Model Discussion}
\label{sec:boundary_model_discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

  myXTable(caption="Scale parameter~($\\theta$), Solow residual~($\\lambda$), 
           and sum of squared errors~($sse$) for all modeling choices.",
           label=paste0("tab:", opts_current$get("label")), 
           digits=c(1,1,1,1,1,1,1, 2, 4, 3))
@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary model discussion}
\label{sec:boundary_model_discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

  myXTable(caption="Scale parameter~($\\theta$), Solow residual~($\\lambda$), 
           and sum of squared errors~($sse$) for all modeling choices.",
           label=paste0("tab:", opts_current$get("label")), 
           digits=c(1,1,1,1,1,1,1, 2, 4, 4))
@
